---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/SAGMM)](https://cran.r-project.org/package=SAGMM)
[![Travis-CI Build Status](https://travis-ci.org/andrewthomasjones/SAGMM.svg?branch=master)](https://travis-ci.org/andrewthomasjones/SAGMM)

# SAGMM

The SAGMM package allows for computation of gaussian mixture models using stochastic approximation to increase efficiency with large data sets. The primary function \code{SAGMMFit} allows this to be performed in a relative flexible manner.

## Installation

You can install SAGMM from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("andrewthomasjones/SAGMM")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SAGMM)
#generate sample data
sims<-generateSimData(ngroups=10, Dimensions=10, Number=10^5)

#time fit
ptm <- proc.time()
res1<-SAGMMFit(sims$X, ngroups=10)
proc.time()-ptm #should be under 15 seconds for 10 x 10^5 dataset on an ordinary laptop
```

```{r example2}
library(SAGMM)
#generate sample data
sims<-generateSimData(ngroups=5, Dimensions=2, Number=10^3)
#plot
res2<-SAGMMFit(sims$X, sims$Y, plot=T)
```